---
title: "MetaP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MetaP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MetaP)
```


## Overall Projects
This function takes between 2 and 5 Data Frames and calculates p-values for each Biomarker to perform one of the 4 pooling tests below on. 

The possible pooling method arguments are:

* "fisher" for Fisher

* "stouffer" for Stouffer

* "min" for Minimum P-value

* "max" for Maximum P-value

Usage: Project(x1, x2, x3, x4, x5, test)


## Check input
This function checks if the inputs are vaild to use in our main function
Checks that:
*All inputs are lists/ Data Frames
*Same number of columns in each Data Frame
*Rows 2 to p are biomarkers
*Checks that the group membership column will take at least two unique values

Usage: Check.input(frames)


## GroupDifference
This function takes a Data Frame that can be normally distributed or not normally distributed. For 2 groups we will perform a two sample t-test or Wilcoxon rank sum test based on Normality. For more than 2 groups we will perform ANOVA or Kruskal Wallis test based on Normality. 

Usage: GroupDifference(x)

The return is an output of pvalues for each biomarker 


## Pool.Fisher
This function sums the log-transformed p-values, following a chi-squared distributions with 2k degrees of freedom

Usage: pool.fisher(x)

The return is a vector of p-values, one for each biomarker

## Pool.Stouffer
This function sums the inverse normal p-values, following a standard normal distribution

Usage: pool.stouffer(x)

The return is a vector of p-values, one for each biomarker

This function follows a beta distribution with degrees of freedom α=1 and β=k

Usage: pool.min(x)

The return is a vector of p-values, one for each biomarker

## Pool.max
This function follows a beta distribution with degrees of freedom α=k and β=1

Usage: pool.max(x)

The return is a vector of p-values, one for each biomarker